Oral contraceptives

### 2021-01-18 r_notebooks/exploring_hydroxychloroquine_sulphate.nb.Rmd
R analyses

```{r hcq-monthly-ts-plot, fig.cap="Total quantity of combined hormonal and progestogen only oral contraceptives prescribed per month."}
hcq %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  tsibble() %>% 
  autoplot(n) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

@@

# plan(multisession)
# # Chunking analyses into ~100 GPs uses ~ 23Gb of RAM
# system.time(hcq_gp_cv_models_1 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[1:100]) %>% 
#               regionalCV(init = 48))
# system.time(hcq_gp_cv_models_2 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[101:200]) %>% 
#               regionalCV(init = 48))
# system.time(hcq_gp_cv_models_3 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[201:300]) %>% 
#               regionalCV(init = 48))
# system.time(hcq_gp_cv_models_4 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[301:length(complete_gp)]) %>% 
#               regionalCV(init = 48))
# plan(sequential)
# 
# hcq_gp_cv_models <- 
#   bind_rows(hcq_gp_cv_models_1,
#             hcq_gp_cv_models_2,
#             hcq_gp_cv_models_3,
#             hcq_gp_cv_models_4)
# 
# hcq_gp_cv_models %>%
#   saveRDS("../data/hcq_gp_cv_models.rds")

>>>>

```{r hcq-monthly-ts-plot, fig.cap="Total quantity of hcq prescribed per month."}
hcq %>% 
  group_by(datename) %>% 
  summarise(n = sum(Quantity)) %>% 
  tsibble() %>% 
  autoplot(n) +
  geom_vline(xintercept = dmy("23-March-2020"), colour = "red") # add line to mark the start of lockdown
```

@@

plan(cluster)
# Chunking analyses into ~100 GPs uses ~ 23Gb of RAM
system.time(hcq_gp_cv_models_1 <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[1:100]) %>%
              regionalCV(init = 48))
system.time(hcq_gp_cv_models_2 <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[101:200]) %>%
              regionalCV(init = 48))
system.time(hcq_gp_cv_models_3 <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[201:300]) %>%
              regionalCV(init = 48))
system.time(hcq_gp_cv_models_4 <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
    filter(regional_unit %in% complete_gp[301:length(complete_gp)]) %>%
              regionalCV(init = 48))
plan(sequential)

hcq_gp_cv_models <-
  bind_rows(hcq_gp_cv_models_1,
            hcq_gp_cv_models_2,
            hcq_gp_cv_models_3,
            hcq_gp_cv_models_4)

hcq_gp_cv_models %>%
  saveRDS("../data/hcq_gp_cv_models.rds")
